Redundant calibration as a complex optimization problem

### 2017-01-12 paper.tex
newest version

\newcommand{\bz}{\bmath{z}}
\newcommand{\bs}{\bmath{s}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bO}{\bmath{O}}
\newcommand{\bP}{\bmath{P}}
\newcommand{\bQ}{\bmath{Q}}
\newcommand{\bR}{\bmath{R}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bmJ}{\bmath{\mathcal{J}}}
\newcommand{\bmH}{\bmath{\mathcal{H}}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

Two ways of speeding up redundant calibration have also been proposed recently. The first technique makes use of the ADI method, in which we alternate between solving the gains, their conjugates and 
the true observed visibilities \citep{Wijnholds2012,Marthi2014}. Note that the fact that \citet{Marthi2014} is making use of the ADI method is not immediately clear
from the paper itself. We will elaborate on this later on in the paper (see Section~\ref{sec:results}). The second is to use the preconditioned conjugate gradient (PCG) method. PCG allows us to exploit the sparsity inherent in the redundant calibration problem, 
to speed it up \citep{Liu2010}. A proper comparison between these two approaches has not been done before.

@@

\section{Results}
\label{sec:results}
In the previous section we discussed the complex GN and LM algorithms and how they relate to redundant calibration. If we inspect Eq.~\eqref{eq:GN_update} and 
Eq.~\eqref{eq:GN_update} we see that the most expensive operation used by the GN and LM algorithms is the inversion of the Hessian $\bH$. The most logical 
way of speeding up the algorithm is to investigate whether we can do this inversion in some efficient way.

Two recent algorithms have been proposed that are able to invert $\bH$ in an efficient manner, namely the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. 
Note that here we focus solely on comparing the computational complexity of inverting $\bH$ using either one of these two methods. Rating the LM or GN algorithms
using one of these approaches relative to each other once the computation complexity of inverting $\bH$ is known is trivial. The simulations we performed to compare these two 
methods are summarized in Section~\ref{sec:simulations}.

@@

The basic difference between these two speedup algorithms can be understood by inspecting Fig.~\ref{fig:hessian}. The first observation we can make by inspecting 
Fig.~\ref{fig:hessian_reg} and Fig.~\ref{fig:hessian_hex} is that the diagonal entries of the Hessians are more significant than the off-diagonal entries.
It therefore makes sense to approximate the $\bH$ (or the modified Hessian $\bmH$) with its diagonal, which greatly simplifies the computational complexity of inverting 
$\bH$, i.e. it becomes $\mathbb{O}(P)$\footnote{The cost of constructing 
the diagonal is not included in this estimate.} \citep{Smirnov2015}. This diagonal-approximation approach is effectively ADI \citep{Marthi2014}. The exact details of this 
approach is discussed in Section~\ref{sec:adi}. We will also show how \citet{Marthi2014}, \citet{Smirnov2015} and \citet{Salvini2014} relate to each other in that same section. It should be noted that the ADI method actually refers to the complete LM update step using the approximate $\bH$ and not just 
to the inversion of the approximate $\bH$. Furhtermore, the name ADI also implies that with this algorithm we alternate between computing the 
gains, their conjugates and the true observed visibilities. %In Appendix~\ref{sec:sbc} we briefly summarize the ADI method that is used for skymodel-based calibration.

@@

Even though the PCG method is computationally more expensive than the ADI method we can not arrive at a final conclusion at this point. With the ADI method 
we only approximate the inverse of the Hessian, while in the case of the PCG method we compute the exact inverse. So the question arises whether the PCG method 
will converge much faster than the ADI method even though each iteration (which includes an inversion) is more expensive. We investigate this question in Section~\ref{sec:comparison}.

@@

The main flow of a single simulation is as follow. We created corrupted visibilities, using either one of the experimental setups summarized in Table~\ref{tab:ch_parm} and
the fixed simulation parameters presented in Table~\ref{tab:fixed_parm}. We then used per time-slot and channel redundant calibration, i.e. we either used the ADI or PCG algorithm, to 
estimate the gains and the true observed visibilities. To obtain statistically significant results we performed, for both the ADI and PCG algorithms, multiple statistical independent simulations.

@@

\begin{table}
\centering
\caption{We generated results using two major experimental setups. We either used one frequency channel and multiple time-slots, or one time-slot and multiple frequency 
channels. The most important parameters used in realizing these two major setups are presented here. Note that we refer to the gain error models in Table~\ref{tab:gain_parm} in the 
last row of this table.}
\begin{tabular}{|c c c|} 
\hline
 & Setup 1 & Setup 2\\
\hline
\hline
 Num. channels & 1024 & 1\\
$\nu$-range & 100-200 MHz & 1.4 GHz\\
Num. timeslots & 1 & 50\\
%Hour angle &-1^h & [-1^h,1^h]\\
Gain error model (Table~\ref{tab:gain_parm}) & 2 & 1\\
\hline
\end{tabular}
\label{tab:ch_parm}
\end{table}

\subsection{Alternating Direction Implicit Method}
\label{sec:adi}
%In Section~\ref{sec:adi} we show how the ADI method used for skymodel-based calibration relates to the redundant ADI method presented in \citet{Marthi2014}.

We start this section by briefly reviewing the ADI method as it pertains to skymodel-based calibration in Section~\ref{sec:sbc} \citep{Salvini2014,Smirnov2015}.
In Section~\ref{sec:red_c} we re-derive the redundant calibration ADI method presented in \citet{Marthi2014}. In \citet{Marthi2014} the ADI method is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught. When derived in this way, its relation to the recent works \citep{Salvini2014,Smirnov2015} are unclear.
We will use the diagonal-approximate approach proposed in \citet{Smirnov2015} to show that the ADI algorithm presented in \citet{Marthi2014} is in actual fact redundant 
\textsc{StEfCal} \citep{Salvini2014}.

\subsubsection{Skymodel-based Calibration}
\label{sec:sbc}
\textsc{StEFCal} is an alternating direction implicit method, in which the measurement equation, Eq.~\eqref{eq:vis_definition}, is linearized by assuming that the gains are known, but
that their conjugates are unknown \citep{Mitchell:MWA-cal,Salvini2014}. Under this assumption, the conjugates of the gains can be obtained trivially. Once the conjugates of the gains have been computed, the gains can be solved for. One can then alternate between computing the gains and their conjugates until convergence
is reached. By correctly exploiting the symmetry inherent in the calibration problem this alternating approach can be replaced by a single iterative new parameter estimation step. \cite{Salvini2014} also show that
the convergence of the algorithm can be improved if for every even iteration the basic new parameter estimation step is modified as follows: the current gain estimate is replaced by the average of the current gain estimate and the gain estimate of the previous odd iteration.
\textsc{StEFCal} lowers the computational complexity of normal skymodel-based calibration from $\mathbb{O}(N^3)$ to $\mathbb{O}(N^2)$.

\citet{Smirnov2015} recently showed that one can also derive \textsc{StEFCal} by viewing normal skymodel-based calibration as a complex optimization problem.
They realized while inspecting the skymodel-based $\bH$ that its diagonal entries are much more significant than its off-diagonal entries.
As we mention in Section~\ref{sec:results}, the exact same conclusion can be reached if we inspect the Hessian $\bH$ that is associated with redundant calibration (see Fig.~\ref{fig:hessian}). 
By approximating the skymodel-based $\bH$ by its diagonal and substituting this approximate Hessian $\widetilde{\bH}$ back into the fundamental skymodel-based LM update step we obtain \citep{Smirnov2015} 
\begin{align}
\breve{\bg}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bg}_k,\label{eq:stef_lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bg}_k, \label{eq:stef_alpha}  
\end{align}

@@

\subsubsection{Redundant Calibration}
\label{sec:red_c}
Since the diagonal entries of the $\bH$ associated with redundant calibration are more significant than its off-diagonal entries it makes 
sense to try and approximate it with its diagonal (see Fig.~\ref{fig:hessian} and Eq.~\eqref{eq:red_H}).
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$.
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Also note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with \textsc{StEfCal}. We have therefore successfully used the diagonal approximation approach proposed by \citet{Smirnov2015} to re-derive the ADI method presented in 
\citet{Marthi2014} and in doing so we have shown that the algorithm in \citet{Marthi2014} is actually redundant StEfCal. We could also have shown this by using the alternating approach 
presented in \citet{Salvini2014}; which explains why, in this paper, we have been referring to the algorithm presented in \citet{Marthi2014} as the ADI method.

@@

Optimality results of ADI were presented in \citet{Marthi2014}. We do not repeat their analysis here. We however, do present our own ADI results in Fig.~\ref{fig:prec_error} that confirm that the
ADI method can accurately estimate the antenna gains and the observed visibilities at different SNR values. To quantity the exact error in our estimates we used the precentage error $\beta$ defined 
as 
\begin{equation}
\label{eq:beta}
\beta = \frac{\sum_{pq} |v_{pq} - \widehat{v}_{pq} |^2}{\sum_{pq} |v_{pq}|^2}.
\end{equation}
We have already defined $v_{pq}$ in Eq.~\eqref{eq:vec_definitions}. Moreover, in Eq.~\eqref{eq:beta}, $\widehat{v}_{pq}$ denotes the ADI estimate of $v_{pq}$.

\begin{figure}
\includegraphics[width=0.47\textwidth]{./prec_error.pdf} 
\caption{We plot the precentage error $\beta$ between the estimated 
predicted visibilities and the true predicted visibilities for different SNR values as a function of the number of antennas in the array $N$. The graph presented here was generated using the first experimental setup in Table~\ref{tab:ch_parm}.}
\label{fig:prec_error}
\end{figure}

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bs}{\bmath{s}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bO}{\bmath{O}}
\newcommand{\bP}{\bmath{P}}
\newcommand{\bQ}{\bmath{Q}}
\newcommand{\bR}{\bmath{R}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bmJ}{\bmath{\mathcal{J}}}
\newcommand{\bmH}{\bmath{\mathcal{H}}}
\newcommand{\bzero}{\bmath{0}}
\newcommand{\bone}{\bmath{1}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

Two ways of speeding up redundant calibration have also been proposed recently. The first technique makes use of the ADI method, in which we alternate between solving the gains, their conjugates and 
the true observed visibilities \citep{Wijnholds2012,Marthi2014}. Note that the fact that \citet{Marthi2014} is making use of the ADI method is not immediately clear
from the paper itself. We will elaborate on this later on in Section~\ref{sec:adi}. The second is to use the preconditioned conjugate gradient (PCG) method. PCG allows us to exploit the sparsity inherent in the redundant calibration problem, 
to speed it up \citep{Liu2010}. A proper comparison between these two approaches has not been done before.

@@

\section{Results}
\label{sec:results}
In Section~\ref{sec:main_sec} we discussed the complex GN and LM algorithms and how they relate to redundant calibration. If we inspect Eq.~\eqref{eq:GN_update} and 
Eq.~\eqref{eq:LM_update} we see that the most expensive operation used by the GN and LM algorithms is the inversion of the Hessian $\bH$. The most logical 
way of speeding up the algorithm is to investigate whether we can do this inversion in some efficient way.

Two recent algorithms have been proposed that are able to invert $\bH$ in an efficient manner, namely the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. 
Note that here we focus solely on comparing the computational complexity of inverting $\bH$ using either one of these two methods. Rating the LM or GN algorithms
using one of these approaches relative to each other once the computational complexity of inverting $\bH$ is known is trivial. The simulations we performed to compare these two 
methods are summarized in Section~\ref{sec:simulations}.

@@

The basic difference between these two speedup algorithms can be understood by inspecting Fig.~\ref{fig:hessian}. The first observation we can make by inspecting 
Fig.~\ref{fig:hessian_reg} and Fig.~\ref{fig:hessian_hex} is that the diagonal entries of the Hessians are more significant than the off-diagonal entries.
It therefore makes sense to approximate the $\bH$ (or the modified Hessian $\bmH$) with its diagonal, which greatly simplifies the computational complexity of inverting 
$\bH$, i.e. it becomes $\mathbb{O}(P)$\footnote{The cost of constructing 
the diagonal is not included in this estimate.} \citep{Smirnov2015}. This diagonal-approximation approach is effectively ADI \citep{Marthi2014}. The exact details of why this 
is the case is discussed in Section~\ref{sec:adi}. We will also show how \citet{Marthi2014}, \citet{Smirnov2015} and \citet{Salvini2014} relate to each other in that same section. It should be noted here that strictly speaking the ADI method actually refers to the complete LM update step using the approximate $\bH$ and not just 
to the inversion of the approximate $\bH$. To improve the readability of the paper, we use the acronym ADI to refer to both the faster approximate inverse approach and the complete LM algorithm that uses it.
Which one of these two concepts we are actually referring to, however, is always perfectly clear from the context.
%Furhtermore, the name ADI also implies that with this algorithm we alternate between computing the 
%gains, their conjugates and the true observed visibilities. %In Appendix~\ref{sec:sbc} we briefly summarize the ADI method that is used for skymodel-based calibration.

@@

Even though the PCG method is computationally more expensive than the ADI method we can not arrive at a final conclusion at this point. With the ADI method 
we only approximate the inverse of the Hessian, while in the case of the PCG method we compute the exact inverse. So the question arises whether the LM algorithm using the PCG method 
will converge much faster than the ADI method even though each iteration (which includes an inversion) is more expensive. We investigate this question in Section~\ref{sec:comparison}.

@@

The main flow of a single simulation is as follow. We created corrupted visibilities, using the fixed simulation parameters presented in Table~\ref{tab:fixed_parm} and either one of the experimental setups summarized in Table~\ref{tab:ch_parm}. We then used per time-slot and channel redundant calibration, i.e. we use the LM algorithm which in turn makes use of either the ADI or PCG method, to 
estimate the gains and the true observed visibilities. To obtain statistically significant results we performed, for both the ADI and PCG methods, multiple statistical independent simulations.

@@

\begin{table}
\centering
\caption{We generated results using two major experimental setups. We either used one frequency channel and multiple time-slots, or one time-slot and multiple frequency 
channels. The most important parameters used in realizing these two major setups are presented here. Note that we refer to the gain error models in Table~\ref{tab:gain_parm} in the 
last row of this table.}
\begin{tabular}{|c c c|} 
\hline
 & Setup 1 & Setup 2\\
\hline
\hline
 Num. channels & 1024 & 1\\
$\nu$-range & 100-200 MHz & 1.4 GHz\\
Num. timeslots & 1 & 50\\
%Hour angle &-1^h & [-1^h,1^h]\\
Gain error model (Table~\ref{tab:gain_parm}) & 2 & 1\\
Initial guess: $\bz_0$ & $\bone$ & $\bone$\\
\hline
\end{tabular}
\label{tab:ch_parm}
\end{table}

\subsection{Alternating Direction Implicit Method}
\label{sec:adi}
%In Section~\ref{sec:adi} we show how the ADI method used for skymodel-based calibration relates to the redundant ADI method presented in \citet{Marthi2014}. 
We start this section by briefly reviewing the ADI method as it pertains to skymodel-based calibration in Section~\ref{sec:sbc} \citep{Salvini2014,Smirnov2015}.

In Section~\ref{sec:red_c}, we re-derive the fast redundant calibration algorithm presented in \citet{Marthi2014} using the complex framework proposed by \citet{Smirnov2015}. In \citet{Marthi2014} it is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught. When derived in this way, its relation to the recent works \citep{Salvini2014,Smirnov2015} are unclear.
To elaborate a little, the conclusion that the algorithm presented in \citet{Marthi2014} is nothing more than a redundant extension of the skymodel-based ADI method (i.e. redundant \textsc{StEfCal}) is in actual fact not obvious either (something we only briefly mentioned in the introduction and then for the sake of simplicity and convenience chose to ignore until now) if the aforementioned 
partial derivative strategy is used to derive it. In Section~\ref{sec:red_c}, we will, therefore, also explicitly show that 
the redundant calibration algorithm presented in \citet{Marthi2014} is in actual fact nothing more than an ADI method and in doing so we will have justified the naming 
convention we have used throughout the paper.

\subsubsection{Skymodel-based Calibration}
\label{sec:sbc}
\textsc{StEFCal} is an ADI method, in which the measurement equation, Eq.~\eqref{eq:vis_definition}, is linearized by assuming that the gains are known, but
that their conjugates are unknown \citep{Mitchell:MWA-cal,Salvini2014}. Under this assumption, the conjugates of the gains can be obtained trivially. Once the conjugates of the gains have been computed, the gains can be solved for. One can then alternate between computing the gains and their conjugates until convergence
is reached. By correctly exploiting the symmetry inherent in the calibration problem this alternating approach can be replaced by a single iterative new parameter estimation step. \cite{Salvini2014} also show that
the convergence of the algorithm can be improved if for every even iteration the basic new parameter estimation step is modified as follows: the current gain estimate is replaced by the average of the current gain estimate and the gain estimate of the previous odd iteration.
\textsc{StEFCal} lowers the computational complexity of normal skymodel-based calibration from $\mathbb{O}(N^3)$ to $\mathbb{O}(N^2)$.

\citet{Smirnov2015} recently showed that one can also derive \textsc{StEFCal} by viewing normal skymodel-based calibration as a complex optimization problem.
They realized while inspecting the skymodel-based $\bH$ that its diagonal entries are much more significant than its off-diagonal entries.
As we mention in Section~\ref{sec:results}, the exact same conclusion can be reached if we inspect the Hessian $\bH$ that is associated with redundant calibration (see Fig.~\ref{fig:hessian}). 
By approximating the skymodel-based $\bH$ by its diagonal and substituting this approximate Hessian $\widetilde{\bH}$ back into the fundamental skymodel-based LM update step we obtain \citep{Smirnov2015} 
\begin{align}
\breve{\bg}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bg}_k,\label{eq:stef_lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bg}_k, \label{eq:stef_alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$.

@@

\subsubsection{Redundant Calibration}
\label{sec:red_c}
Since the diagonal entries of the $\bH$ associated with redundant calibration are more significant than its off-diagonal entries it makes 
sense to try and approximate it with its diagonal (see Fig.~\ref{fig:hessian} and Eq.~\eqref{eq:red_H}).
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k. \label{eq:alpha}  
\end{align}
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Also note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with \textsc{StEfCal}. We have therefore successfully used the diagonal approximation approach proposed by \citet{Smirnov2015} to re-derive the fast redundant calibration method presented in 
\citet{Marthi2014} and in doing so we have shown that this algorithm is in actual fact nothing more than the ADI method (i.e. redundant \textsc{StEfCal}), which justifies the naming convention we have been using for this method. We could also have shown this same result by using
a more direct approach. We could simply have used the alternating strategy presented in the skymodel-based ADI paper itself \citep{Salvini2014}.

@@

Optimality results of ADI were presented in \citet{Marthi2014}. We do not repeat their analysis here. We however, do present our own ADI results in Fig.~\ref{fig:prec_error} that confirm that the
ADI method can accurately estimate the antenna gains and the observed visibilities at different SNR values. To quantity the exact error in our estimates we used the percentage error $\beta$ defined 
as 
\begin{equation}
\label{eq:beta}
\beta = \frac{\sum_{pq} |v_{pq} - \widehat{v}_{pq} |^2}{\sum_{pq} |v_{pq}|^2}.
\end{equation}
We have already defined $v_{pq}$ in Eq.~\eqref{eq:vec_definitions}. Moreover, in Eq.~\eqref{eq:beta}, $\widehat{v}_{pq}$ denotes the ADI estimate of $v_{pq}$.

\begin{figure}
\includegraphics[width=0.47\textwidth]{./prec_error.pdf} 
\caption{We plot the percentage error $\beta$ between the estimated 
predicted visibilities and the true predicted visibilities for different SNR values as a function of the number of antennas in the array $N$. The graph presented here was generated using the first experimental setup in Table~\ref{tab:ch_parm}.}
\label{fig:prec_error}
\end{figure}
